CF Registry Analysis

### 2023-06-02 Christine Chan/CF Registry/cf_registry_analysis.qmd
CFRD registry

annual <- read.csv("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/CFF19_Annualized_Del1.csv",na.strings = c("", "N/A")

@@

demogs = read.csv("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/CFF19_DemogCFDiag_Del1.csv")

@@

    select(eDWID,Age_YrEnd,Gender,MutClass,A_IsOnEnzymes,A_FEV1_pct_predicted,

>>>>

annual <- read.csv("~/Documents/Work/Christine Chan/CF registry data/CFF19_Annualized_Del1.csv",na.strings = c("", "N/A")

@@

demogs = read.csv("~/Documents/Work/Christine Chan/CF registry data/CFF19_DemogCFDiag_Del1.csv")

@@

    select(eDWID,Age_YrEnd,Gender,MutClass,A_IsOnEnzymes,A_FEV1,A_FEV1_pct_predicted,
